Client-Side Indexes for Fast Full-Text Searching

### 2014-12-11 paper/paper.tex
add figures to paper

In this section, we explain the overall goals and architecture of Lucy.js, how it fits into IndexedDB, as well as give further details of our implementation.

@@

@@

@@

\section{Evaluation}

>>>>

In this section, we explain the overall goals and architecture of the Lucy.js system, how it fits into IndexedDB, as well as give further details of our implementation.

\begin{figure}[]
   \includegraphics[scale=.43]{arch}
  \caption{caption here.}
\end{figure}

@@

\begin{figure}[h!]
   \includegraphics[scale=.53]{query-times}
  \caption{caption here}
\end{figure}

@@

\section{Evaluation and Applications}

@@

\begin{figure}[h!]
   \includegraphics[scale=.53]{demo_results}
  \caption{caption here.}
\end{figure}
